---
title: OSRM areas
format: gfm
knitr:
  opts_chunk: 
    fig.path: figs/
---

```{r include=F}
knitr::opts_chunk$set(
  cache = T, 
  warning = F
)
```

# Installation

```{r}
# install.packages('remotes')
# remotes::install_github('d2cml-ai/osrmareas')
```

# Usage

```{r dep}
library(osrmareas)
library(ggplot2)
library(dplyr)
```

The `osrmareas` package provides functions for working with OSRM routes and generating area polygons. Here's an example of how to use the package:

```{r a1}
lat <- -9.0686007
lon <- -78.5891182

# Get routes inside a specified radius
routes <- get_routes_inside(lat, lon, radius_km = 2, grid_size = 0.300)
routes
```

The `get_routes_inside` function retrieves routes within a given radius from a specified latitude and longitude. It returns a dataframe with the routes information.

```{r p1}
# Plot the routes on a map
p1 <- 
  ggplot(routes) + 
  geom_sf() + 
  coord_sf() +
  theme_minimal()
p1
```

You can visualize the routes using `ggplot2` and the `geom_sf` function.

Filter points inside 2km radius:

```{r p2}
km_max <- 2
routes_km <- routes |> 
  dplyr::filter(distance < km_max) 

p2 <- 
  routes_km |> 
  ggplot() +
  geom_sf() +
  theme_minimal()
p2
```

This code filters the routes within a maximum distance of 2km and plots them on a map.

Generate a polygon shapefile:

```{r a2}
area1 <- 
  get_area(routes_km, km_max, concavity = 1) 
area2 <- 
  get_area(routes_km, km_max, concavity = 2)

area1 |> 
  ggplot() +
  geom_sf()
area2 |> 
  ggplot() +
  geom_sf()
```

The `get_area` function generates a polygon shapefile based on the filtered routes within a specified maximum distance and concavity level.

Routes inside the area:

```{r p3}
bind_rows(area1, area2) |> 
  mutate(concavity = row_number() |> factor()) |> 
  ggplot() +
  geom_sf(aes(color = concavity), fill = NA) +
  geom_sf(data = routes_km, color = "grey80") +
  geom_point(aes(lon, lat)) +
  labs(title = "Area between 2km (car)") +
  theme_minimal() 
```

This code plots the generated area polygons along with the filtered routes inside the area. The `concavity` level is used to differentiate the polygons, and the original routes are shown in grey.

Please note that you need to have the necessary packages installed and loaded (`osrmareas`, `ggplot2`, `dplyr`) in order to run the code successfully.
